---
title: "Zenith angle and sunlight"
author: "Pedro J. Aphalo"
date: "6 April 2015"
output: html_document
---

## Set up
```{r}
library(photobiology)
library(photobiologyInOut)
library(photobiologygg)
```

```{r}
options(photobiology.radiation.unit = "photon")
```

## Data from TUV

The TUV model (Version 5.0) was run in batch mode and without summary
calculations.

        TUV inputs:
        ==================================================================
        inpfil =      usrinp   outfil =      usrout   nstr =            16
        lat =          0.000   lon =          0.000   tmzone =         0.0
        iyear =         2014   imonth =           3   iday =            21
        zstart =       0.000   zstop =       80.000   nz =              81
        wstart =     290.000   wstop =      760.000   nwint =          940
        tstart =      12.000   tstop =       18.000   nt =              13
        lzenit =           F   alsurf =       0.100   psurf =       -999.0
        o3col =      300.000   so2col =       0.000   no2col =       0.000
        taucld =       0.000   zbase =        4.000   ztop =         5.000
        tauaer =       0.235   ssaaer =       0.990   alpha =        1.000
        dirsun =       1.000   difdn =        1.000   difup =        0.000
        zout =         0.000   zaird =   -9.990E+02   ztemp =     -999.000
        lirrad =           T   laflux =           F   lmmech =           F
        lrates =           T   isfix =            0   nms =              0
        ljvals =           F   ijfix =            0   nmj =              0
        iwfix =            0   itfix =            0   izfix =            0
        ==================================================================
        ==== Spectral weighting functions used:
        ==== Photolysis reactions used:
        ==================================================================
         Discrete ordinates           16 -stream radiative transfer
         air temperature: USSA, 1976
         air concentrations: USSA, 1976
         ozone profile: USSA, 1976
         DATAE1/SUN/susim_hi.flx
         DATAE1/SUN/atlas3_1994_317_a.dat
         DATAE1/SUN/neckel.flx
         DATAE1/SUN/sao2010.solref.converted
         aerosols:  Elterman (1968) continental profile
        step =    1 sza =     1.827 Earth-sun factor =  1.0077450
        step =    2 sza =     5.711 Earth-sun factor =  1.0077339
        step =    3 sza =    13.207 Earth-sun factor =  1.0077206
        step =    4 sza =    20.707 Earth-sun factor =  1.0077095
        step =    5 sza =    28.208 Earth-sun factor =  1.0076983
        step =    6 sza =    35.710 Earth-sun factor =  1.0076849
        step =    7 sza =    43.211 Earth-sun factor =  1.0076739
        step =    8 sza =    50.712 Earth-sun factor =  1.0076628
        step =    9 sza =    58.213 Earth-sun factor =  1.0076495
        step =   10 sza =    65.715 Earth-sun factor =  1.0076385
        step =   11 sza =    73.216 Earth-sun factor =  1.0076274
        step =   12 sza =    80.718 Earth-sun factor =  1.0076140
        step =   13 sza =    88.219 Earth-sun factor =  1.0076028

```{r}
zangles.spct <- 
  read_tuv_file(file = "usrout2.txt", 
                unit.out = "photon", 
                date = ymd("2014-03-21"))
```


## Spectra

```{r, fig.height=8, fig.width=8}
plot(zangles.spct, annotations = "colour.guide") + 
  facet_wrap(~angle)
```

## Summaries

```{r}
zangles.summaries <-
  zangles.spct[ , .(ppfd =    q_irrad(.SD, PAR()) * 1e6, 
                    UVA.PAR = q_ratio(.SD, UVA(), PAR()), 
                    UVB.PAR = q_ratio(.SD, UVB(), PAR()), 
                    B.G =     q_ratio(.SD, Blue("Sellaro"), Green("Sellaro")), 
                    R.FR =    q_ratio(.SD, Red("Smith"), Far_red("Smith")),
                    angle =   .SD$angle[1],
                    date =    .SD$date[1]
                    ), 
              by = spectrum]
```

```{r, fig.height=3, fig.width=5}
ggplot(zangles.summaries, aes(x = angle, y = ppfd)) + geom_line() + ylim(0, NA)

```

```{r, fig.height=3, fig.width=5}
ggplot(zangles.summaries, aes(x = angle, y = UVA.PAR * 1e3)) + geom_line() + ylim(0, NA)

```

```{r, fig.height=3, fig.width=5}
ggplot(zangles.summaries, aes(x = angle, y = UVB.PAR * 1e3)) + geom_line() + ylim(0, NA)

```

```{r, fig.height=3, fig.width=5}
ggplot(zangles.summaries, aes(x = angle, y = B.G)) + geom_line() + ylim(0, NA)

```

```{r, fig.height=3, fig.width=5}
ggplot(zangles.summaries, aes(x = angle, y = R.FR)) + geom_line() + ylim(0, NA)

```
