---
title: "Accessing the Quick TUV calculator"
subtitle: "Package 'photobiologyInOut' `r packageVersion('photobiologyInOut')` "
author: "Pedro J. Aphalo"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: yes
vignette: >
  %\VignetteIndexEntry{Accessing the Quick TUV calculator}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

Package 'photobiologyInOut' since 2018, versions (>= 0.4.15), has supported the
import of the output files from interactively run spectral simulations done in
the Quick TUV calculator, as exemplified in the User Guide. 

In versions (>= 0.4.29) it is also possible to call the Quick TUV calculator
server directly from within R, to get the spectral data returned in a
`source_spct` object or in  a `source_mspct` ready to be used with functions
from the R for Photobiology suite, or used as data frames with other R code.
Examples demostrating this new feature need to access the UCAR server, and
because of this, they included in this article, that is part of the on-line
documentation, but not distributed as part of the package.

The implementation of the interaction with the server is inspired on that used
in package 'foqat'. This is actually very simple: to construct URLs identical to
those generated by the [Quick TUV calculator web interface] and use them to
download the computed spectral data into a file. This file is already in a
format supported by function `read_qtuv_txt()` avaialble in package
'photobiologyInOut' (>= 0.4.15).

```{r, include = FALSE}
library(knitr)
opts_chunk$set(fig.align='center', fig.show='hold',
               fig.width=7, fig.height=6, size="footnotesize")
```

```{r setup}
library(photobiologyInOut)
library(ggspectra)
library(lubridate)

theme_set(theme_bw() + theme(legend.position = "top"))
```

## Simulation of a single spectrum

In the first example, using default arguments for all parameters except `time`,
the text returned by the sever is saved into a temporary file, the data read
into a `source_spct()` and the file deleted. The default for `sun.elevation` is
`NULL` and the sun elevation is compute from the geographic coordinates and time
coordiantes.

```{r}
sun_greenwich.spct <- 
  qtuv_s.e.irrad(time = ymd_hm("2024-06-23 12:00", tz = "UTC"))
colnames(sun_greenwich.spct)
```

Variable `s.e.irrad` corresponds to the total down-welling spectral irradiance. Variable `s.e.irrad.dir` is direct, `s.e.irrad.diff.down` is down-welling diffuse radiation and `s.e.irrad.diff.up` is up-welling diffuse radiation.
 
The summary shows in addition to a summary of the data, some impotant metadata. 

```{r}
summary(sun_greenwich.spct)
```

```{r}
cat(comment(sun_greenwich.spct))
```

```{r}
what_measured(sun_greenwich.spct)
```

```{r}
when_measured(sun_greenwich.spct)
```

```{r}
how_measured(sun_greenwich.spct)
```

```{r}
where_measured(sun_greenwich.spct)
```

```{r}
attr(sun_greenwich.spct, "qtuv.url")
```

```{r}
autoplot(sun_greenwich.spct)
```

To save the raw output from TUV into a persistent file, we have to provide a file name. We also extend the wavelength range, and provide the coordinates of a different location.

```{r}
my.geocode <- data.frame(lon = 24.96474, lat = 60.20911)
```

```{r}
sun_viikki.spct <- 
  qtuv_s.e.irrad(time = ymd_hm("2024-06-23 12:20", tz = "EET"),
                 w.length = 290:800,
                 geocode = my.geocode,
                 file = "qtuv-viikki-test.txt")

summary(sun_viikki.spct)
```

The file was not deleted as a file name was supplied.

```{r}
file.exists("qtuv-viikki-test.txt")
```

The spectrum was also imported into R as a `source_spct` object for which
an `autoplot()` method is defined in package 'ggspectra'.

```{r}
autoplot(sun_viikki.spct)
```

```{r}
autoplot(sun_viikki.spct, unit.out = "photon")
```

## Simulation of a collection of spectra

Not to abuse the use of the UCAR server, the examples in this section create collections of very few spectra. The functions do not impose any strict limit but keep in mind that the recommended maximum is 100 spectra per user and day.

Four different ozone column thicknesses.

```{r}
sun_viikki_ozone.mspct <- 
  qtuv_m_s.e.irrad(
    time = ymd_hm("2024-06-23 12:20", tz = "EET"),
    ozone.du = c(200, 250, 300, 350),
    w.length = 290:450,
    geocode = my.geocode
  )

summary(sun_viikki_ozone.mspct)
autoplot(sun_viikki_ozone.mspct, 
         range = c(NA, 340), 
         annotations = c("-", "peaks"))
```

Three sun elevation angles above the horizon in degrees. Geographic and time
coordinates are used to compute the sun elevation angle when the angle is not
supplied as in other examples, but if the angle is passed as an argument, they
are ignored.

```{r}
sun_viikki_elevation.mspct <- 
  qtuv_m_s.e.irrad(
    sun.elevation = c(60, 40, 20),
    w.length = 290:450,
    geocode = my.geocode
  )

summary(sun_viikki_elevation.mspct)
autoplot(sun_viikki_elevation.mspct)
```

Three different times of the day.

```{r, fig.height=12}
sun_viikki_time.mspct <- 
  qtuv_m_s.e.irrad(
    time = ymd_hm("2024-06-23 12:20", tz = "EET") +
      hours(c(0, 3, 6)),
    w.length = 290:750,
    geocode = my.geocode
  )

summary(sun_viikki_time.mspct)
autoplot(sun_viikki_time.mspct, facets = 1)
```

Three different latitudes.

```{r}
my.geocodes <- data.frame(lat = c(30, 50, 70),
                          lon = rep(25, 3))
my.geocodes[["address"]] <- 
  paste("lat", my.geocodes[["lat"]], sep = ".")
```

```{r, fig.height=12}
sun_latitudes.mspct <- 
  qtuv_m_s.e.irrad(
    time = ymd_hm("2024-06-23 12:20", tz = "EET"),
    w.length = 290:750,
    geocode = my.geocodes
  )

summary(sun_latitudes.mspct)
autoplot(sun_latitudes.mspct, facets = 1)
```

Two different cloud conditions.

```{r}
my.clouds <- qtuv_clouds(c("clear.sky", "cirrus"))
```

```{r, fig.height=8}
sun_viikki_clouds.mspct <- 
  qtuv_m_s.e.irrad(
    time = ymd_hm("2024-06-23 12:20", tz = "EET"),
    w.length = 290:750,
    geocode = my.geocode,
    clouds = my.clouds
  )

summary(sun_viikki_clouds.mspct)
autoplot(sun_viikki_clouds.mspct, facets = 1)
```

For three times, as above, but keeping the downloaded files, by passing a file name "root".

```{r, fig.height=12}
sun_viikki_time.mspct <- 
  qtuv_m_s.e.irrad(
    time = ymd_hm("2024-06-23 12:20", tz = "EET") +
      hours(c(0, 3, 6)),
    w.length = 290:750,
    geocode = my.geocode,
    file = "qtuv-viikki"
  )

summary(sun_viikki_time.mspct)
autoplot(sun_viikki_time.mspct, facets = 1)
```
